Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-31 notes/2epsilon/main.tex
rename folder
Update notes/2epsilon/main.tex

\begin{thm}
\label{thm_gamma_smooth}
$S_\beta(\dataobs)$ is $\gamma -$smooth sensitivity for $\hellinger(\bysinfer(\dataobs),-)$ if it is calculated by:
\begin{equation}
  \label{eq_smooth}
   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs')} +\gamma \cdot d(\dataobs,\dataobs')} \bigg \},
\end{equation}
where $d$ is the Hamming distance between two data sets.
\end{thm}

\begin{proof}
of Theorem. \ref{thm_gamma_smooth}.
For $\adj{\dataobs}{\dataobs'}$ and arbitrary $\dataobs'' \in \{0,1\}^{n}$:

@@

\begin{equation*}
\begin{split}
& \leq \frac{1}{LS(\dataobs'')} +\gamma \cdot (1 + d(\dataobs',\dataobs''))\\
& = \gamma + \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\\
& = \gamma + \frac{1}{S(\dataobs')}
\end{split}
\end{equation*}

@@

\begin{definition}
\label{def_smoo}
The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset\dataobs$ with probability
\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
{\nomalizer{\dataobs}}.
\end{equation*}
where $S_\beta(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by Theorem \ref{thm_gamma_smooth}.
\end{definition}

@@

\begin{proof} of Lemma \ref{lem_hexpmech_privacy}.
  By Definition \ref{def_epsilon_delta_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:

>>>>

\begin{thm}
\label{thm_gamma_smooth}
$S(\dataobs)$ is $\gamma -$smooth sensitivity if it is calculated by:
\begin{equation}
  \label{eq_smooth}
   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs')} +\gamma \cdot d(\dataobs,\dataobs')} \bigg \},
\end{equation}
where $d$ is the Hamming distance between two data sets.
\end{thm}

\begin{proof}
of Theorem. \ref{thm_gamma_smooth}.

For $\adj{\dataobs}{\dataobs'}$ and arbitrary $\dataobs'' \in \{0,1\}^{n}$:

@@

\begin{equation*}
\begin{split}
& \leq \frac{1}{LS(\dataobs'')} +\gamma \cdot (1 + d(\dataobs',\dataobs''))\\
& = \gamma + \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\\
& = \gamma + \frac{1}{S(\dataobs')}
\end{split}
\end{equation*}
$\implies$
\begin{equation*}
\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.
\end{equation*}

@@

\begin{definition}
\label{def_smoo}
The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset\dataobs$ with probability
\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
{\nomalizer{\dataobs}}.
\end{equation*}
where $S(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by Theorem \ref{thm_gamma_smooth}.
\end{definition}

@@

\begin{proof} of Lemma \ref{lem_hexpmech_privacy}.

  By Definition \ref{def_epsilon_delta_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:
